---
output:
  pdf_document: default
  html_document: default
---
Within this project, I would like to explore the  CoinGecko API and the package "geckor" in R.
Then I would collect the current and historical cryptocurrency market data for a coin using the public 'CoinGecko' API and do a Arima forecast.

```{r setup, include=FALSE, fig.width=8, fig.height=8}
library(geckor)
library(dplyr)
library(tseries)
library(forecast)
library(Metrics)
library(ggplot2)
```


Let's use bitcoin as an example here. First, I want to obtain historical data for bitcoin.
The function "coin_history" can retrieve coin-specific market data for the last n days. If  open-high-low-close price data is needed, use function "coin_history_ohlc" instead.


```{r}
r <- coin_history(coin_id = "bitcoin", vs_currency = "usd", days = "max")
r
```

Since we only need timestamp and price from obtained data, I save them in a dataframe
and convert it to timeserie formatt for later use. So now df has all daily market price
for bitcoin.

```{r}
var <- c("timestamp", "price")
df <- r[var]
df <- df[c(1:nrow(df) - 1),]
df <- ts(df["price"], start = c(2013,4,28), frequency = 365)
```

Now, let's define the training and testing period. I will use the last 7 days as 
testing set and all other historical data as training set.

```{r}
n = nrow(df)
n1 = nrow(df) - 6
n2 = nrow(df) - 7

df_train = ts(df[c(4:n2),])
df_test = ts(df[c(n1:n),])
df_full = ts(df[c(4:n),])
```

We now need to check the stationary of our data. We need a unstationary data because 
a stationary time series is one whose properties do not depend on the time at which the 
series is observed. We can do that with the Augmented Dickey-Fuller Test.

H0: The time series is non-stationary. 
H1: The time series is stationary.
Since the p-value is not less than .05, we fail to reject the null hypothesis.
This means the time series is non-stationary. our data is depend on the time at 
which the series is observed.

```{r}
adf.test(df_full)
```
We will run the auto.arima function on our training data, which will help us to forecast
next 7 days market price and prediction intervals. 

```{r}
model <- auto.arima(df_train)
fcast <- forecast(model, h = 7, level = 95)

fcast
```

let's create a table of predicted price and actual price.

```{r}
result <- cbind(df_test,as.numeric(fcast$mean))
colnames(result) <- c("Actual","Predicted")
result
```

Now, let's get the Metrics MAPE which is used to judge the performance of the model.
we have a mape of 12.49%, which means the average deviation between the forecasted value 
and actual values was 12.49%.

```{r}
mape <- mape(df_test,as.numeric(fcast$mean))

mape*100
```

Lastly plot the historical price for bitcion, certainly the price has been jumping insane
last few years.

```{r}
autoplot(fcast) + (labs(y = "Price", x = "Days"))
```